Create Walkover of Brief Names

### 2022-04-08 data-cleaning/04-create-walkover-brief-name.Rmd
write correct df to box

```{r}
join_data <- author_level %>% select(id = BoxFileID, name_incorrect = AmicusBrief, CaseId)
join_data$id <- as.character(join_data$id)

@@

```{r}
check_in_amicus <- amicus %>% left_join(data, by = c('brief' = 'name_correct'))
june_russo_fix <- check_in_amicus %>% filter(is.na(name_incorrect)) %>%
  select(brief) %>% unique()
```

@@

```{r}
box_write(data,
           file_name = "walkover_brief_names.csv",
           dir_id = 145990409196)
```

>>>>

```{r}
# select id's from author data
join_data <- author_level %>%
  select(id = BoxFileID, name_incorrect = AmicusBrief, CaseId, AmBriefID)

join_data$id <- as.character(join_data$id)

@@

Add our updated brief id

```{r}
amicus_current_ids <- amicus %>% select(brief, brief_id = id)
final <- data %>% 
  left_join(amicus_current_ids, c("name_correct" = "brief")) %>% 
  select(new_id=brief_id, case_code = CaseId, brief_code = AmBriefID,
         name_correct, name_incorrect, old_id = id)

final %>% filter(is.na(new_id)) # this brief doesn't exist in our data ?
final %>% head()
```

## June v Russo

Read in the June v Russo names from Holly's data file.

```{r}
jvr_incorrect <- box_read_excel("941695019313", sheet="final") %>% 
  mutate(brief_id = as.character(brief_id))
jvr_incorrect %>% head()
```

Get the "correct" june v russo brief names

```{r}
jvr_correct <- amicus %>% filter(grepl("June", brief)) %>%
  mutate(id = as.character(id)) %>% 
  select(new_id=id,name_correct=brief)
```

Join the two

```{r}
jvr <- jvr_correct %>% left_join(jvr_incorrect, c("new_id"="brief_id"))

jvr <- jvr %>% 
  mutate(old_id = 0,
         case_code = 999999) %>% 
  select(new_id, case_code, brief_code, name_correct, name_incorrect=amicus, old_id)
```

Add to final df

```{r}
final <- final %>% rbind(jvr) %>%
  distinct(new_id, case_code, brief_code, name_correct, name_incorrect, old_id)
```

Check

```{r}
final %>% nrow()
```

## Save

@@

```{r}
box_write(final,
           file_name = "walkover_brief_names.csv",
           dir_id = 145990409196)
```
